---
title: "Landreth Final Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    sidebar:
      width: 250
---



```{r setup, include=FALSE}
library(flexdashboard)

```

## Introduction {.sidebar}

```{css}
.sidebar {
  max-width: 300px; /* Adjust the maximum width as needed */
  word-wrap: break-word;
}
```
Preparing the dashboard based on the instructions given at @magallanes_reyes_data_2022, and @sievert_flexdashboard_2022

`---`

### References
```{css}
.sidebar {
  max-width: 300px; /* Adjust the maximum width as needed */
  word-wrap: break-word;
}
```
- Aden-Buie, Garrick, Carson Sievert, Richard Iannone, JJ Allaire, and Barbara Borges. 2023. "Flexdashboard: R Markdown Format for Flexible Dashboards." Manual. https://pkgs.rstudio.com/flexdashboard/.
- Magallanes Reyes, José Manual. 2022. Data Visualization for Social and Policy Research: A Step-by-Step Approach Using R and Python. Cambridge: Cambridge University Press


```{r}
# Load plots
salary_plot <- readRDS("~/GitHub/Landreth_Final/salary_plot.rds")
education_level_plot <- readRDS("~/GitHub/Landreth_Final/education_level_plot.rds")
age_experience_plot <- readRDS("~/GitHub/Landreth_Final/age_experience_plot.rds")
salary_map_plot <- readRDS("~/GitHub/Landreth_Final/salary_map_plot.rds")
```

# Top Paying Jobs

```{r}
salary_plot
```



# Education Levels

```{r}
education_level_plot
```


# Salary by Age & YOE
```{r}
age_experience_plot

```


# Salary Map

```{r}
salary_map_plot

```

